Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Adjust abstract

\begin{abstract}
We present an approach to automatically discover analytic population models for gravitational-wave (GW) events from data.
As more gravitational-wave (GW) events are detected, flexible models such as Gaussian Mixture Models have become more important in fitting the distribution of GW properties due to their expressivity.
However, flexible models come with a cost: a large number of parameters that lack physical motivation, making interpreting the implication of these models very difficult.
In this work, we demonstrate the use of symbolic regression to distill such flexible models into interpretable analytic expressions.
We recover common GW population models such as a power-law-plus-Gaussian, and find a new empirical population model which combines accuracy and simplicity.
This demonstrates a promising pathway to automatically discover interpretable descriptions of features in the ever-growing GW catalog. 
\end{abstract}

>>>>

\begin{abstract}
We present an automatic approach to discover analytic population models for gravitational-wave (GW) events from data.
As more gravitational-wave (GW) events are detected, flexible models such as Gaussian Mixture Models have become more important in fitting the distribution of GW properties due to their expressivity.
However, flexible models come with many parameters that lack physical motivation, making interpreting the implication of these models challenging.
In this work, we demonstrate the use of symbolic regression to distill such flexible models into interpretable analytic expressions.
We recover common GW population models such as a power-law-plus-Gaussian, and find a new empirical population model which combines accuracy and simplicity.
This demonstrates a promising pathway to discover interpretable population models, automatically, from the GW merger catalogs and other astrophysical phenomena.
\end{abstract}
